---
title: "MIDTERM PROJECT"
author: "Andrew Sisitzky,Chen Xu,Guangze Yu,Yuyang Li"
date: "20201 November 1"
output: 
  revealjs::revealjs_presentation:
    #template: hw_temp_1.html
    theme: sky
    highlight: pygments 
    #css: reveal.css
---


```{r setup, include=FALSE}
library(png)
library(grid)
library(knitr)
source("eda.R")
opts_chunk$set(echo = TRUE)
```




# 

<div style= "align:center; font-size:80px;">
<p><br><br><b>
DATA WRANGLING 
</b>
</p>

</div>


## Data clean-Strawberries.csv
 - Take apart strawberries.csv and restructure, 
 - Use <i><b>Year, State, Domain, Chemical, Chemical type, Value, units </i></b>as variable to get a new table
 
 - Select data when<i><b> Domain = "CHEMICAL"</i></b>
 
## Data clean-Strawberries.csv

 - Empty rows were removed to make the data more compact
 
 - The name of various pesticides were converted to uppercase letters for later matching

## Data wrangling-left_join

 - Function <i>left_join</i> is used to match the data by <i><b>"chemicaltype = pesticide" </i></b> 
 
 - Combine them into one table for subsequent EDA
 
 - Delete the missing value if <i><b>"Year = NA"</i></b>


</section>

# 
<div style= "align:center; font-size:80px;">
<p><br><br><b>
MAKE JUDGEMENTS
</b>
</p>

</div>


## Give a number for toxins

 - <b>For human</b>
    + Carcinogen:<i>known=4,probable=3,possible=2,unknown=1</i>
    
    + Hormone.Disruptor:<i>suspected=2,unknown=1</i>
    
    + Neurotoxins:<i>present=2,unknown=1</i>
    
    + Developmental/ReproductiveToxins:<i>present=2,unknown=1</i>
    

 -  <b>For bee</b>
 
    + Bee.Toxins:<i>high=4,moderate=3,slight=2,unknown=1</i>
    
## Calculate total toxins
 -  <b>For human</b>
 
    + Toxicity for human = <i>Carcinogen+HormoneDisruptor+Neurotoxins+ Developmental or Reproductive Toxins</i>
     
 -  <b>For bee</b>
 
    + Toxicity for bee = <i>Bee.Toxins</i>  
  


</section>
# 
<div style= "align:center; font-size:80px;">
<p><br><br><b>
EDA
</b>
</p>

</div>


## Choose data to plot

 - Select chemical types exist in <i><b>Pesticides.csv</i></b>
 
 - Filter dataframe into subsets in different measurements
    + MEASURED IN LB / ACRE / YEAR  AVG
    + MEASURED IN PCT OF AREA BEARING  AVG
    + MEASURED IN LB
    + MEASURED IN LB / ACRE / APPLICATION  AVG
    + MEASURED IN NUMBER  AVG

## EDA PLOT 1

 - Looking at the average lbs of strawberries harvested per acre in each state.Added color to show the toxicity level of each observation. 
 
 - It appears that the harvests with higher lbs per acre also tend to be treated with chemicals that are rated higher by out <i><b>'toxicitylevelhuman'</i></b> variable.
 
 
## 
```{r}
edaplot <- ggplot(data=chemical_clean_lbperacre,mapping=aes(x=State,y=Value))+geom_point(mapping=aes(color=toxicitylevelhuman))+scale_color_gradient(low="blue", high="red")+theme(axis.text.x = element_text(angle = 90))
edaplot 
```


## EDA Plot 2

 - Adding the <b>mean toxicity</b> of all observations in each state to the map.  
 
 - This plot shows that, based on this dataset, the harvests in Oregon tended to use chemicals that were rated higher by our toxicity scale in comparison to other states.
 
##

```{r}
edaplot2 <- ggplot() +geom_polygon( data=eda_subset, aes(x=long, y=lat, group=group,fill = mean_toxicity), color="white",size = 0.2)
edaplot2
```

</section>



